Predicting the Housing Market using \\ Multiple Linear Regression

### 2023-12-04 manuscript/Manuscript.tex
added assumption plots

\title{Predicting the Housing Market using \\ Linear Regression}

@@

\bigskip
\noindent{\sc Keywords}:
housing market;
natural language processing;
linear regression;
model predictions

@@

>>>>

\title{Predicting the Housing Market using \\  Multiple Linear Regression}

@@

\bigskip
\noindent{\sc Keywords}:
housing market prediction;
model predictions;
multiple linear regression;
natural language processing

@@

asgfsgdfsgjdfg\cite{CFA}

\begin{figure}[h!]
    \caption{Linearity Check}
    \includegraphics[width=1\textwidth]{linearity_check.pdf}
    \label{fig:linearity_check}
\end{figure}

\begin{figure}[h!]
    \caption{Homoskedasticity Check}
    \includegraphics[width=1\textwidth]{homoskedasticity_check.pdf}
    \label{fig:homoskedasticity_check}
\end{figure}

\begin{figure}[h!]
    \caption{Residuals Distribution}
    \includegraphics[width=1\textwidth]{residuals_distribution.pdf}
    \label{fig:residuals_distribution}
\end{figure}
